Can We Formalise Type Theory Intrinsically without Any Compromise?

### 2025-12-03 tex/CPP26/final/main.tex
ACM wants us to cite the formalisation

\paragraph{Formalisation} Our formalisation can be found at \url{https://github.com/L-TChen/TTasQIIRT}, or archived with DOI \href{https://doi.org/10.5281/zenodo.17802827}{10.5281/zenodo.17802827}.

@@

\begin{acks}
  We appreciate the comments from the anonymous reviewers, which improved the results of the paper and the formalisation in several ways.
  We are also grateful to Shu-Hung You for his comments on an early draft.
  The work is supported by the National Science and Technology Council of Taiwan under grant NSTC 114-2222-E-001-001-MY3, and the Engineering and Physical Sciences Research Council
  (EP/Y000455/2).

  All data underpinning this publication are openly available from
  \href{https://doi.org/10.5281/zenodo.17802827}{doi:10.5281/zenodo.17802827}.
\end{acks}

@@

%%% Local Variables:
%%% mode: latex
%%% TeX-master: "main.tex"
%%% eval: (add-hook 'after-save-hook (lambda () (shell-command "make tex")) t)
%%% End:

>>>>

\paragraph{Formalisation} Our formalisation~\cite{formalisation} can be found at \url{https://github.com/L-TChen/TTasQIIRT}, or archived with DOI \href{https://doi.org/10.5281/zenodo.17802827}{10.5281/zenodo.17802827}.

@@

\begin{acks}
  We appreciate the comments from the anonymous reviewers, which improved the results of the paper and the formalisation in several ways.
  We are also grateful to Shu-Hung You for his comments on an early draft.
  The work is supported by the National Science and Technology Council of Taiwan under grant NSTC 114-2222-E-001-001-MY3, and the Engineering and Physical Sciences Research Council
  (EP/Y000455/2).
\end{acks}

\section*{Data-Availability Statement}

All data underpinning this publication are openly available from
Zenodo~\cite{formalisation} with DOI \href{https://doi.org/10.5281/zenodo.17802827}{10.5281/zenodo.17802827}.

@@
